Figures main manuscript

### 2019-07-15 code/figures.rmd
Only include panel a) of Figure 3 in the main manuscript
Cleaned up figures file

---
title: "Figures"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: 
  pdf_document: 
    latex_engine: xelatex
---

@@

##Figure 1
```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

##Figure 2
```{r Density_plot, cache = TRUE}

#1) I2 plot----
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(Heterogeneity = "Observed")

I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#2) tau2 plot----

dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
names(dens_tau2) <-  sort(unique(dat$effect))

# Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>%
 bind_rows(.id = "effect") %>%
 rename(Heterogeneity = tau_index) %>%
 mutate(Heterogeneity = recode(Heterogeneity,
                             '1' = "Zero",
                             '2' = "Small",
                             '3' = "Medium",
                             '4' = "Large"),
          Heterogeneity = as.factor(Heterogeneity),
        tau = sqrt(tau2_hat))

# Observed tau2 estimates, i.e, results from main table, see table.rmd
# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
observed_tau <- dat %>%
   split(.$effect) %>%
   map(transform_MA) %>% 
   map_dfr(summarizer, .id = "effect") %>%
   select(effect, tau2) %>%
   mutate(Heterogeneity = "Observed",
          tau = sqrt(tau2))

tau_plot <- ggplot(tau2_dist, aes(x = tau, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed_tau, aes(y = ..density.., x = tau), bins = 130, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 0.25)) + #truncate plot for better visualization
  scale_fill_brewer(palette = "Dark2",
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_color_brewer(palette = "Dark2",
                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
       legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)," estimate", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

#3) combine I2-tau2-density-plots----
densities <- plot_grid(I2_plot, tau_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities

# save_plot("../figures/densities_het.png", densities,
#            nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
```

Figure 2. Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects. For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108. Each simulated density consists of approximately 370,000 estimates.

##Figure 3, correlations per effect type
```{r corr_per_effect_type, cache = FALSE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

@@

labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>%
  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting

#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

>>>>

---
title: "Figures main manuscript"
author: "Heterogeneity in direct replications in psychology and its association with effect size"
output: 
  pdf_document: 
    latex_engine: xelatex
---

@@

##Figure 1

```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

##Figure 2

```{r Density-plot-prep, cache = TRUE}
#1) I2 plot----
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(Heterogeneity = "Observed")
```

```{r Density-plot, fig.height=4, fig.width=6.47}
I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2",
                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  scale_color_brewer(palette = "Dark2", 
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

I2_plot
# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())

Figure 2. Simulated $I^2$  densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 37 effects. Each simulated density consists of approximately 370,000 estimates.

##Figure 3, correlations per effect type

```{r corr_per_effect_type-prep, cache = TRUE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

@@

labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>%
  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
```

```{r corr_per_effect_type-plot, cache = FALSE}
#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

#This section gives the correlations reported in the section 'Heterogeneity and effect sizes' in the main manuscript
